\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-01-18 concepts.tex
updates

Our system, \texttt{T-REX} (or the Teleo-Reactive EXecutive) is an
adaptive, artificial intelligence based controller and provides
general framework for building reasoning systems for real-world
autonomous vehicles. At MBARI \texttt{T-REX} is used for AUV control;
another instantiation of the system is being used for control of a
terrestrial personal robot \cite{pr2}. The development of
\texttt{T-REX} has been targeted at surveying a number of
oceanographic features which are dynamic and unpredictable
spatio-temporally. Typically this requires our AUVs to balance the
goals of coverage spatially while opportunistically following features
of scientific interest and to do so while being operationally aware of
its own limitations in terms of resources (typically the battery state
of charge) and overall proximity to other observational assets for
obtaining scientific ground-truth. We are therefore interested in
representational frameworks that allow robots to pursue long-term
objectives while choosing short-term gain and can gracefully deal with
exogenous or endogenous change.

To enable this responsiveness to external observations, the agent has
to be able to synthesize plans insitu and to re-plan. We use a
temporal constraint-based planner EUROPA$_2$ with a demonstrated
legacy of having flown on NASA space missions
\cite{Jonsson00,bresina05}. Our autonomy architecture brings three key
innovations for AUV adaptation: the use of flexible plan
representations, compositional control with the use of partitioned
networks and off-line learning to inform insitu environmental state
estimation. In this section we detail some of the key concepts
relevant to flexible plan representation. Section \ref{sec:arch} has
details the \texttt{T-REX} partitioned architecture and estimation
driven vehicle adaptation.

% \texttt{T-REX} uses EUROPA$_2$ a constraint-based temporal planner
% \cite{Jonsson00,Frank2003} developed for NASA missions, most recently
% for the Mars Exploration Rovers \cite{bresina05}.

@@

Traditionally robot execution has relied on dispatching commands at
precise times. Such linear sequences of precisely timed commands give
no ability to adjust execution on the basis of sensory
information. Although some commands can issue tests on sensor
readings, these tests have the objective of verifying whether expected
execution conditions are occuring. If not, the state of the system is
declared off-nominal and execution of the sequence of commands is
interrupted. More recently, executives have been proposed and
implemented that significantly broaden the way robots can be commanded
\cite{mus98,Alami:1998p820}. For example, the Remote Agent executive
interpreted a \textit{temporally flexible plan} which represents each
start time as a variable and contains an explicit network of bounded
delay constraints between such variables.

>>>>

Our system, \texttt{T-REX} (or the Teleo-Reactive EXecutive) is an
adaptive, artificial intelligence based controller and provides
general framework for building reasoning systems for real-world
autonomous vehicles. At MBARI \texttt{T-REX} is used for AUV control;
another instantiation of the system is being used for control of a
terrestrial personal robot \cite{pr2, Meeussen:2010dn}. The development of
\texttt{T-REX} has been targeted at surveying a number of
oceanographic features which are dynamic and unpredictable
spatio-temporally. Typically this requires our AUVs to balance the
goals of coverage spatially while opportunistically following features
of scientific interest and to do so while being operationally aware of
its own limitations in terms of resources (typically the battery state
of charge) and overall proximity to other observational assets for
obtaining scientific ground-truth. We are therefore interested in
representational frameworks that allow robots to pursue long-term
objectives while choosing short-term gain and can gracefully deal with
exogenous or endogenous change.

To enable this responsiveness to external observations, the agent has
to be able to synthesize plans insitu and to re-plan. We use a
temporal constraint-based planner EUROPA$_2$ with a demonstrated
legacy of having flown on NASA space missions
\cite{jonsson00,bresina05}. Our autonomy architecture brings three key
innovations for AUV adaptation: the use of flexible plan
representations, compositional control with the use of partitioned
networks and off-line learning to inform insitu environmental state
estimation. In this section we detail some of the key concepts
relevant to flexible plan representation. Section \ref{sec:arch} has
details the \texttt{T-REX} partitioned architecture and estimation
driven vehicle adaptation.

@@

Traditionally robot execution has relied on dispatching commands at
precise times. Such linear sequences of precisely timed commands give
no ability to adjust execution on the basis of sensory
information. Although some commands can issue tests on sensor
readings, these tests have the objective of verifying whether expected
execution conditions are occuring. If not, the state of the system is
declared off-nominal and execution of the sequence of commands is
interrupted. More recently, executives have been proposed and
implemented that significantly broaden the way robots can be commanded
\cite{mus98,alami:1998p820}. For example, the Remote Agent executive
interpreted a \textit{temporally flexible plan} which represents each
start time as a variable and contains an explicit network of bounded
delay constraints between such variables.
